---
title: "Activity 1.2 - RStudio and R Markdown"
author: "Matt Phad"
date: "8/29/2019"
output: html_document
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

A data frame with 1846 rows and 3 columns. The 3 variables are *dataset*, *x*, and *y*.



### Exercise 2

First let's plot the data in the dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

First let's plot the data in the **star** dataset:

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Next we calculate the correlation coefficient, *r*:

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```
This correlation coefficient for the **star** dataset is very similar to that of the **dino** dataset.


### Exercise 4

First let's plot the data in the **circle** dataset:

```{r plot - circle}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

Next we calculate the correlation coefficient, *r*:

```{r cor - circle}
circle_data %>%
  summarize(r = cor(x, y))
```
Once again, the correlation coefficient for this dataset, **circle** is very close to that of the **dino** dataset.


### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.)